---
title: "class_1_english"
subtitle: "⚔<br/>with xaringan"
author: "Onkar Singh"
institute: "Shri Ram Global School"
date: "2021/11/23 (updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r echo = FALSE}
library(xaringan)
# install.packages("devtools")
# devtools::install_github("gadenbuie/xaringanExtra")
library(xaringanExtra)
```


```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```


```{r , echo=FALSE}
library(xaringanthemer)

style_duo(
  primary_color = "#1F4257",
  secondary_color = "#F97B64",
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "300", "300i"),
  code_font_google   = google_font("Fira Mono")
)
```

---
class: inverse, center, middle

# Word Test

---


# Word    Synonyms

.pull-left[

- Answer  =   reply

- ask = question

- begin = start

- blend = mix

- calm = quiet

- cool = cold

- difficult = hard

- decide = choose

- eager = keen

- easy = simple

- fear = fright 

- fair  = just

- fast = quick ]


.pull-right[

- fly = wing

- gross = rude

- have = gain 

- idea = thought

- keep  = hold

- listen = hear

- neat = tidy ]


---
class: inverse, center, middle

# Final Exam English 17th March 2022 (Thursday)

## 11.30am to 12.30pm

## Ms. Jaslin Narang

## 774 629 8158

## Gulmohar
## Grammar
## Creative Writing
---
class: inverse, center, middle
Gulmohar
# Chapter 10: The King's Drum 
---
class: inverse, center, middle
Grammar:
Ch-11 Am/Is/Are (to be verbs)

---
class: inverse, center, middle
Grammar:
Ch-14 Has/Have (have verbs)

---
class: inverse, center, middle
Grammar:
Ch-21 In/On/Under/Between (Prepositions of place)

---
class: inverse, center, middle
Creative writing:
Reading comprehension.

---
class: inverse, center, middle
Creative writing:
Picture composition
